\subsection*{Warm Welcome}

\vspace{0.5cm}

Welcome to \emph{Muktware Ubuntu Manual}. This manual is intended to provide a complete comprehensive guide about \emph{Ubuntu 12.04 LTS}. This manual is intended for both users new to Ubuntu coming from other operating systems and power users moving in from Ubuntu 10.04.  This manual was built with the help of the community for the community. From the point of view of the user, this manual strives to provide a complete picture of the glorious world of Ubuntu. It takes the user on a journey by helping him to get acquainted with Ubuntu, until the stage where he is able to manage all by himself. It all begins first with a short introduction about Ubuntu. Why Ubuntu in the first place? It then covers everything starting from installing Ubuntu to customizing Ubuntu. You are not solely limited to this manual alone. The manual also provides information about where to find information in case you run into problems and need help troubleshooting. Tips are provided to encourage the user to try out new ways of performing stuff. \\

\vspace{0.3cm}

\par \noindent I would like to thank Jasna Ben\v{c}i\'{c} for her contributions in writing many chapters of this manual with patience and perseverance. I would also like to thank Brett Legree for his works in the customising Ubuntu and advanced topics section. A special thanks to Swapnil Bhartiya for creating the awesome cover page of this manual. I would also like to thank the Ubuntu Documentation Team whose work were borrowed in some sections of this manual. And finally, I would like to thank Michael Hall whose works were used in chapter \ref{chap:other-users}. You can find his original work \href{http://mhall119.com/2012/04/so-you-want-to-try-switching-to-ubuntu/}{here}. These people were our first contributors and certainly not our last. \\

\vspace{0.3cm}

\par \noindent  Last but not least, please be aware that this is the very first edition and hence is a work in progress. Despite our best effort to remove typos, they always still creep in. If you find any mistakes or improvements please contact us at \href{mailto:ubuntu@muktware.com}{ubuntu@muktware.com}. We intend to bring future editions which would bring corrections and perhaps also cover more topics.\\

\vspace{0.3cm}

\par \noindent I hope you enjoy using this manual as much as we enjoyed working on it for you. \\

\vspace{0.7cm}

\par \noindent Nekhelesh Ramananthan 
\par \noindent Ubuntu Editor 
\par \noindent Muktware
